{{< var titll >}}

### 2024-07-07 index.qmd
abc
templated

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
filters:
  - webr
#format: 
#  html:
#    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
#    include-in-body:
#          - text: |
#              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
---

@@

>>>>

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
filters:
  - webr
---

@@

This is a webR-enabled code cell in a Quarto HTML document.

```{webr-r}
fit = lm(mpg ~ am, data = mtcars)
summary(fit)
```

Abc
